%-*-latex-*-
\input{thispreamble}

This is a closed-book, no compiler, 5 minute quiz.

%------------------------------------------------------------------------------
\nextq
T or F:
\\
The value \verb!5! in the following expression is
type promoted from an \verb!int! to a \verb!double!.
\begin{console}[fontsize=\small]
7 / 3.1 - 2 * 5
\end{console}
\ANSWER
\begin{answercode}
T
\end{answercode}

%------------------------------------------------------------------------------
\nextq
In the following expression, some operators are \verb!int!
operators and others are \verb!double! operators.
\begin{console}[fontsize=\small]
1 + 2 * 4 / 2.0 - 4 / 5 + 7.2 + 1.2
\end{console}
What is the number of \verb!int! operators and the number of
\verb!double! operators?
If you think there are \verb!3! \verb!int! operators and
\verb!4! \verb!double! operators, write \verb!5 3! with
exactly one space between the two integers.
\\
\ANSWER
\begin{answercode}
5 3
\end{answercode}

%------------------------------------------------------------------------------
\nextq
Write down the output when
\verb!5! and \verb!8! are entered as inputs:
\begin{console}[fontsize=\small]
// Area of right-angle triangle
double base = 0.0, height = 0.0;
std::cin >> base >> height;
std::cout << (1 / 2) * base * height << std::endl;
\end{console}
\ANSWER
\begin{answercode}
0
\end{answercode}

%------------------------------------------------------------------------------
\nextq
T or F.
The following code fragment is incorrect since
(1) a \verb!double! variable can only hold a \verb!double! value
and not an \verb!int! value, and
(2) an \verb!int! variable can only hold an \verb!int! value
and not a \verb!double! value.
\begin{console}[fontsize=\small]
double x = 42;
int y = 3.14;
\end{console}
\ANSWER
\begin{answercode}
F
\end{answercode}

%------------------------------------------------------------------------------
\input{thispostamble}
