%-*-latex-*-
\input{thispreamble}

This is a closed-book, no compiler, 5 minute quiz.

%------------------------------------------------------------------------------
\nextq
Complete the following truth table:
\begin{longtable}{|c|c||c|}\hline
 \verb!x!	& \verb!y! 	& \verb!x! \verb!&&! \verb!y! \\ \hline
 \verb!true!	& \verb!true!	& (a)                         \\ \hline
 \verb!true!	& \verb!false!  & (b)                         \\ \hline
 \verb!false!	& \verb!true!   & (c)                         \\ \hline
 \verb!false!   & \verb!false!  & (d)                         \\ \hline
\end{longtable}
\vspace{-0.2cm}
If you think the values (of (a), (b), (c), (d)) are
\verb!true false true false! (respectively), you
write
\verb!true false true false! in that order with exactly one space between
consecutive values.
\\
\ANSWER
\begin{answercode}
true false false false
\end{answercode}

%------------------------------------------------------------------------------
\nextq
Complete the following truth table for \verb!||!
\begin{longtable}{|c|c||c|}\hline
\verb!x!       & \verb!y!      & \verb!x! \verb!||! \verb!y! \\ \hline
\verb!true!    & \verb!true!   & (a) \\ \hline
\verb!true!    & \verb!false!  & (b) \\ \hline
\verb!false!   & \verb!true!   & (c) \\ \hline
\verb!false!   & \verb!false!  & (d) \\ \hline
\end{longtable}
If you think the values (of (a), (b), (c), (d)) are
\verb!true false true false! (respectively), you
write
\verb!true false true false! in that order with exactly one space between
consecutive values.
\\
\ANSWER
\begin{answercode}
true true true false
\end{answercode}

%------------------------------------------------------------------------------
\nextq
Complete the following truth table for \verb@!@
\begin{longtable}{|c||c|}\hline
\verb!x! & \hspace{0.15 in} \verb{!x{ \hspace{0.15 in}      \\ \hline
\verb!true!	 & (a) \\ \hline
\verb!false!     & (b) \\ \hline
\end{longtable}
If you think the values (of (a), (b)) are
\verb!true true! (respectively), you
write
\verb!true true! in that order with exactly one space between
consecutive values.
\\
\ANSWER
\begin{answercode}
false true
\end{answercode}

%------------------------------------------------------------------------------
\nextq
Evaluate the following boolean expression
\[
          \verb@true || false && (!true && true)@
\]
\ANSWER
\begin{answercode}
true
\end{answercode}

%------------------------------------------------------------------------------
\input{thispostamble}
